Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing

### 2020-03-25 paper/eccv2020submission.tex
Adding some exmaple images

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/pred}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/pred.png}  
  \end{subfigure}
\end{figure}

@@

>>>>

\begin{figure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_x}

  \end{subfigure}  
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_constant_y}

  \end{subfigure}
  \begin{center}
    Constant model
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_x_1}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_y_1}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_x_2}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/single_speed_y_2}  
  \end{subfigure}

  \begin{center}
    Images form the inflow speed model. The upper two are from simulation with $g=1.3$ and the lower ones form simulation with $g=0.1$
  \end{center}

  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, x-velocity fields}
      \includegraphics[width=1\linewidth]{imgs/single_fluid_x_1}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, y-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_1}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, x-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_x_2}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    % \caption{Fluid model, y-velocity fields}
    \includegraphics[width=1\linewidth]{imgs/single_fluid_y_2}
  \end{subfigure}

  \begin{center}
  Images form the viscosity-density model. The upper two are from simulation with $\nu=1.3, \rho=2.3$ and the lower ones form simulation with $\nu=1.3, \rho=2.3$
  \end{center}

  \caption{Each image haw tow halves and the upper one shows the ground truth simulation frame. The lower half is the prediction of the model. In the left column, the images are from the x-velocity fie4ld of the simulation and in the right --- form the y-velocity field.}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_1}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_1}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_5}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_5}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_10}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_10}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_15}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_15}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_20}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_20}  
  \end{subfigure}

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/x_step_25}  
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{imgs/sims/constant/y_step_25}  
  \end{subfigure}

  \caption{These frames are generated by the constant model. The artifacts become apparent after the 10.\@ one.}
\end{figure}
